Risk Perceptions for Wearable Devices

### 2015-04-13 tex-inputs/intro.tex
remove low-quality news citations/superfluous citations (there was almost two pages of citations..)

Wearable devices offer many compelling opportunities for benefiting users.  For instance, they could enable more natural, human-centered interface experiences and healthier, fitness-data inspired lifestyles. There will likely be many more applications in the future that take advantage of data captured by wearable devices. However, wearable devices also bring new potential privacy and security risks that could expose users' activities without their awareness or consent. Even though wearable technology is currently in early stages, we have already seen manifestations of these risks. For instance, Fitbit's default privacy settings inadvertently exposed information about some of their users' sexual activity~\cite{Fitbit}, resulting in the inadvertent disclosure of sensitive information. Public discomfort toward facial recognition caused Google to prohibit Google Glass applications from using facial recognition~\cite{GlassDetection}, and public concerns about privacy may have partly contributed to Google's discontinuation of Glass~\cite{14_dvorak_2014,1_russell_2014, 15_mashable_2014, 16_gross_2014}.

Similar privacy~\cite{kelley2013privacy, sadeh2009understanding, shklovski2014leakiness} and security issues~\cite{enck2011study, felt2011survey} pervade smartphones. Mobile platforms have tried to address the risks by communicating data capture to users. However, many users are habituated to these notifications, because they see them frequently, often for things that they do not care about~\cite{felt2012android}. Once habituated to seemingly benign privacy and security warnings, users tend to ignore more sensitive warnings that are similarly designed~\cite{Egelman08}.

>>>>

Wearable devices offer many compelling opportunities for benefiting users.  For instance, they could enable more natural, human-centered interface experiences and healthier, fitness-data inspired lifestyles. There will likely be many more applications in the future that take advantage of data captured by wearable devices. However, wearable devices also bring new potential privacy and security risks that could expose users' activities without their awareness or consent. Even though wearable technology is currently in early stages, we have already seen manifestations of these risks. For instance, Fitbit's default privacy settings inadvertently exposed information about some of their users' sexual activity~\cite{Fitbit}, resulting in the inadvertent disclosure of sensitive information. Public discomfort toward facial recognition caused Google to prohibit Google Glass applications from using facial recognition~\cite{GlassDetection}, and public backlash may have partly contributed to Google's discontinuation of Glass~\cite{1_russell_2014, 16_gross_2014}.

Similar privacy and security issues pervade smartphones. Mobile platforms have tried to address the risks by communicating data capture to users. However, many users are habituated to these notifications, because they see them frequently, often for things that they do not care about~\cite{felt2012android}. Once habituated to seemingly benign privacy and security warnings, users tend to ignore more sensitive warnings that are similarly designed~\cite{Egelman08}.

### 2015-04-13 tex-inputs/methodology.tex
remove low-quality news citations/superfluous citations (there was almost two pages of citations..)

\section{Methodology}
To obtain a comprehensive list of possible risks that wearable devices might present in the future, we examined the sensors, capabilities, permissions, and applications of the most popular wearable devices on the market. At the time of this study, August 2014, the most popular wearable devices included the Fitbit fitness tracker, which continuously monitors heartbeat, steps taken, and sleep patterns~\cite{6_fitbit_2014, 7_time_2014}; the Pebble smartwatch, which can take pictures, send texts, show notifications from online, and push notifications to services~\cite{pebble_smartwatch_2014, 9_verge_2014, 10_readwrite_2014}; and Google Glass~\cite{11_wikipedia_2015, 12_turi_2014}. We used these wearable devices, along with other comparable wearable devices on the market, as inspiration to develop a list of security and privacy risks that users might be concerned about.

>>>>

\section{Methodology}
To obtain a comprehensive list of possible risks that wearable devices might present in the future, we examined the sensors, capabilities, permissions, and applications of the most popular wearable devices on the market. At the time of this study, August 2014, the most popular wearable devices included the Fitbit fitness tracker, which continuously monitors heartbeat, steps taken, and sleep patterns;
%~\cite{6_fitbit_2014, 7_time_2014}
the Pebble smartwatch, which can take pictures, send texts, show notifications from online, and push notifications to services; %~\cite{pebble_smartwatch_2014, 9_verge_2014, 10_readwrite_2014}
and Google Glass %~\cite{11_wikipedia_2015, 12_turi_2014}. 
We used these wearable devices, along with other comparable wearable devices on the market, as inspiration to develop a list of security and privacy risks that users might be concerned about.
